Further Explorations of \suldiox~Aqueous Adsorption:

### 2011-11-30 Background.tex
Conclusions! Finishing up the final edits before handing over to Geri.

Hydrated \suldiox~clusters have been studied extensively with many recent experiments and computations forming a clearer picture of \suldiox~bulk and surface behaviors.\cite{Baer2010, Tarbuck2005, Tarbuck2006, Ota2011, Bishenden1998, Hirabayashi2006, Steudel2009, Yang2002, Hayashi1985, Moin2011, Eckl2008} At a water surface, it is now known that \suldiox~forms a complex with water during adsorption, and then subsequently absorbs into the interfacial region by reaction to form ionic sulfur species.\cite{Tarbuck2005, Tarbuck2006, Ota2011} The first attempt to elucidate the structure of surface hydrated \suldiox~by Baer et al. showed that the bonding coordination distributions of \suldiox~are altered relative to the bulk region, and that two coordinations dominate the distribution of bonding types: the ``SO'' and the ``SOO''. In the same work they then focused on the dominant coordination to determine the most likely cluster geometry using two and three-water clusters bound to the \suldiox. However, none of the studies have yet focused directly on the presence of an extended hydrating structure involving closed rings of molecular interactions involving the solvated \suldiox~molecules.

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/double-cycle-type2-small.png}
		\caption{During the course of MD, the covalent and intermolecular bonds between a \suldiox~and the hydrating waters may form into a ring, resulting in a cyclic hydrate structure. Depicted here is one example of such a cyclic structure, formed by the covalent SO and OH bonds of the two molecule types, and the intermolecular hydrogen bonds, and S-O$_{H_2O}$ interactions. The atoms involved are the S (yellow), O (red), and H (white).}
		\label{fig:cyclic-example}
	\end{center}
\end{figure}

\subsection {Graph Theoretical Details}
The optimized geometry of the \suldiox-hydrates suggests cyclic bonding structures, but it remains a different story entirely when \suldiox~is placed in a dynamic environment such as in the course of MD simulations of an aqueous surface. Geometry optimization shows the formation of these cyclic hydrate structures with two or three waters in a static vacuum. Do the cyclic structures also form in the course of a dynamic bonding process on a simulated water surface, where extended hydrating structures influence \suldiox~and water behavior? To study the formation and behavior of cyclic hydrate structures we employ graph theoretical techniques on MD trajectory data. Previous use of graphs in molecular computations were applied to finding stable arrangements of water clusters, ice, hydrogen bonding, extracting topological molecular properties, and cyclic structure studies.\cite{Anick2002, Huber2007, Radhakrishnan1991, Shi2005, Garcia2004, McDonald1998}

Here we briefly introduce graph theoretical concepts. They have been described well by others with varied application to cyclic structures.\cite{Tutte1984, Balakrishnan2000, Harary1973, Huber2007, Garcia2004, Dury2001} A graph consists of nodes, and edges that connect the nodes. A molecule can be represented with atoms as nodes, and edges for each intramolecular covalent bond connecting the atoms. The set of edges is then further expanded to include intermolecular interactions such as hydrogen bonds and other bonding interactions. Edges may be assigned weights (i.e. bond lengths), types, and can be directional, i.e. pointing towards a target node from a source node. A molecular system including all atoms, bonds, and interactions is thus fully described by a graph.

To detect cyclic structures in a graph a depth-first or breadth-first search (DFS and BFS, respectively) may be used.\cite{Knuth1997, Cormen 2001} A BFS is a recursive algorithm of queuing nodes and all neighboring nodes while performing a specified procedure on each visited node. This is easily performed on adjacency list or connectivity matrix data structures, iterating through nodes (i.e. atoms) of interest in the graph as starting points of the search. In BFS terminology, all nodes are colored during graph traversal to distinguish unvisited nodes (white), queued nodes (gray), and visited nodes (black). Using a BFS on a graph, cyclic structures are detected any time a ``gray target'' is encountered when queuing adjacent neighbors of a node. A benefit of BFS on a graph is the ability to determine the smallest cyclic structure containing a given node. In the case of \suldiox~hydrate structures, beginning the BFS with the \suldiox-sulfur as the starting, or root node for the search, will discover cyclic bonding structures in order of size. Here we are only concerned with the smallest cyclic structure involving those waters in the first and second hydration shells around the \suldiox. Furthermore, it is possible to reconstruct a cycle's structure by finding its size (number of contributing atoms), and the number of unique waters in the cycle. This allows us to distinguish between various types of cyclic structures encountered.

@@

Baer et al. presented a detailed geometric and spectroscopic breakdown of type \Rmnum{3} cycles with two and three waters from their DFT calculations.\cite{Baer2010} Given the information of the number of waters, atoms, and bonds involved in the bonding cycles, we find that of the three-water type \Rmnum{3} cycles, there exist two structural varieties, shown in Figure \ref{fig:type-3-varieties}, that differ in the set of water atoms involved in the cyclic structure. Type \Rmnum{3}-A (shown in Figure \ref{fig:type-3-varieties}A) is arranged with each water contributing an OH bond to the structure of the cycle. Type \Rmnum{3}-B involves a single water contributing an OH, whereas the other two waters contribute only the oxygen atom or the entire water molecule to the structure, respectively. This nuance of the type \Rmnum{3} structures involving three waters, and the overall distribution are presented in more detail later. We also show the distribution of cyclic structures encountered during MD simulations to further understand the behaviors of \suldiox-hydrates at the water surface.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/triple-cycle-types-small.png}
		\caption{Type \Rmnum{3} cyclic structures (see Figure \ref{fig:cyclic-structures}) are found to occur in two varieties that are distinguished by the water atoms contributing to the cyclic structure. In ``type A'' the cycle is formed by an OH bond contributed by each water, and the SO bond of the \suldiox. ``type B'' involves an oxygen atom from one water, an OH bond from a second water, and all atoms of the third water.}
		\label{fig:type-3-varieties}
	\end{center}
\end{figure}

>>>>

Hydrated \suldiox~clusters have been studied extensively with many recent experiments and computations forming a clearer picture of \suldiox~bulk and surface behaviors.\cite{Baer2010, Tarbuck2005, Tarbuck2006, Ota2011, Bishenden1998, Hirabayashi2006, Steudel2009, Yang2002, Hayashi1985, Moin2011, Eckl2008, Jayne1990, Jayne1990a, Donaldson1995} At a water surface, it is now known that \suldiox~forms a complex with water during adsorption, and then subsequently absorbs into the interfacial region by reaction to form ionic sulfur species.\cite{Tarbuck2005, Tarbuck2006, Ota2011} The first attempt to elucidate the structure of surface hydrated \suldiox~by Baer et al. showed that the bonding coordination distributions of \suldiox~are altered relative to the bulk region, and that two coordinations dominate the distribution of bonding types: the ``SO'' and the ``SOO''. In the same work they then focused on the dominant coordination to determine the most likely cluster geometry using two and three-water clusters bound to the \suldiox. However, none of the studies have yet focused directly on the presence of an extended hydrating structure forming closed rings of molecular interactions involving the solvated \suldiox~molecules.

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/double-cycle-type2-small.png}
		\caption{During the course of MD, the covalent and intermolecular bonds between a \suldiox~and the hydrating waters may form into a ring, resulting in a cyclic hydrate structure. Depicted here is one example of such a cyclic structure, formed by the covalent SO and OH bonds of the two molecule types, the intermolecular hydrogen bonds, and S-O$_{H_2O}$ interactions. The atoms involved are the S (yellow), O (red), and H (white).}
		\label{fig:cyclic-example}
	\end{center}
\end{figure}

\subsection {Graph Theoretical Details}
The optimized geometry of the \suldiox~hydrates suggests cyclic bonding structures, but it remains a different story entirely when \suldiox~is placed in a dynamic environment such as in the course of MD simulations of an aqueous surface. Geometry optimization shows the formation of these cyclic hydrate structures with two or three waters in a static vacuum. Do the cyclic structures also form in the course of a dynamic bonding process on a simulated water surface, where extended hydrating structures influence \suldiox~and water behavior? To study the formation and behavior of cyclic hydrate structures we employ graph theoretical techniques on MD trajectory data. Previous use of graphs in molecular computations were applied to finding stable arrangements of water clusters, ice, hydrogen bonding, extracting topological molecular properties, and cyclic structure studies.\cite{Anick2002, Huber2007, Radhakrishnan1991, Shi2005, Garcia2004, McDonald1998}

Here we briefly introduce graph theoretical concepts. They have been described well by others with varied application to cyclic structures.\cite{Tutte1984, Balakrishnan2000, Harary1973, Huber2007, Garcia2004, Dury2001} A graph consists of nodes, and edges that connect the nodes. A molecule can be represented with atoms as nodes, and edges for each intramolecular covalent bond connecting the atoms. The set of edges is then further expanded to include intermolecular interactions such as hydrogen bonds and other bonding interactions. Edges may be assigned weights (i.e. bond lengths), types, and can be directional, i.e. pointing from a source node towards a target node. A molecular system including all atoms, bonds, and interactions is thus fully described by a graph.

To detect cyclic structures in a graph a depth-first or breadth-first search (DFS and BFS, respectively) may be used.\cite{Knuth1997, Cormen 2001} A graph search is a recursive algorithm of queuing nodes and all neighboring nodes while performing a specified procedure on each visited node. This is easily performed on adjacency list or connectivity matrix data structures, iterating through nodes (i.e. atoms) of interest in the graph as starting points of the search. In graph search terminology, all nodes are colored during graph traversal to distinguish unvisited nodes (white), queued nodes (gray), and visited nodes (black). Performing a BFS on a graph, cyclic structures are detected any time a ``gray target'' is encountered when queuing adjacent neighbors of a node. A benefit of BFS is the ability to determine the smallest cyclic structure containing a given node. In the case of \suldiox~hydrate structures, beginning the BFS with the \suldiox-sulfur as the starting, or root node for the search, will discover cyclic bonding structures in order of size. Here we are only concerned with the smallest cyclic structure involving those waters in the first and second hydration shells around the \suldiox. Furthermore, it is possible to reconstruct a cycle's structure by finding its size (number of contributing atoms), and the number of unique waters in the cycle. This allows us to distinguish between various types of cyclic structures encountered.

@@

Baer et al. presented a detailed geometric and spectroscopic breakdown of type \Rmnum{3} cycles with two and three waters from their DFT calculations.\cite{Baer2010} Given the information of the number of waters, atoms, and bonds involved in the bonding cycles, we find that of the three-water type \Rmnum{3} cycles, there exist two structural varieties, shown in Figure \ref{fig:type-3-varieties}, that differ in the set of water atoms involved in the cyclic structure. Type \Rmnum{3}-A (shown in Figure \ref{fig:type-3-varieties}A) is arranged with each water contributing an OH bond to the structure of the cycle. Type \Rmnum{3}-B involves a single water contributing an OH, whereas the other two waters contribute only the oxygen atom or the entire water molecule to the structure, respectively. This nuance of the type \Rmnum{3} structures involving three waters, and the overall distribution of structures are presented in more detail later. We also show the distribution of cyclic structures encountered during MD simulations to further understand the behaviors of \suldiox-hydrates at the water surface.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/cycles/triple-cycle-types-small.png}
		\caption{Type \Rmnum{3} cyclic structures (see Figure \ref{fig:cyclic-structures}) are found to occur in two varieties that are distinguished by the water atoms contributing to the cyclic structure. In ``type A'' the cycle is formed by an OH bond contributed by each water, and the SO bond of the \suldiox. ``Type B'' involves an oxygen atom from one water, an OH bond from a second water, and all atoms of the third water.}
		\label{fig:type-3-varieties}
	\end{center}
\end{figure}

### 2011-11-30 Coordination-Results.tex
Conclusions! Finishing up the final edits before handing over to Geri.

During the course of each simulation, the \suldiox~bonding coordination was determined and recorded for each timestep. From the coordination data we extract not only the populations of the various bonding coordinations, but also the frequencies of transitions between the different coordinations (i.e. the number of times each \suldiox~switched from one coordination type to another). With this data we have generated the directed graphs of Figure \ref{fig:coordination-transitions} depicting the cold and hot (Figure \ref{fig:coordination-transitions} A and B, respectively) bonding coordinations as circular colored nodes.\cite{Ellson2004,Gansner1999} The transitions between the coordinations are depicted as directed edges pointing in the direction of the transition from one coordination to another. The populations of the coordinations are depicted by both the node size and coloration (larger and darker red coordinations occur more frequently). Populations of the transitions between coordinations are depicted by arrow thickness, with thicker lines corresponding to more frequent transitions. Additionally, the transition lines are numbered to the right of each line with the number of times each transition occurred.

@@

As expected for the more populated coordinations, there are more transitions between larger nodes in Figure \ref{fig:coordination-transitions} than transitions to less populated coordinations. Insights to the bonding process are made clearer from these graphs. In the cold system graph of Figure \ref{fig:coordination-transitions}A, we find that the majority of transitions are between the ``S-SO'' and ``SO-SOO'' nodes. The number of transitions within this ``S-SO-SOO'' group of coordinations is an order of magnitude larger than any other transition. This indicates that while the \suldiox~is bound in any of the three most populated bonding coordinations, it is actively binding and unbinding the oxygens to form the other two coordinations in this group. Clearly, the \suldiox~is rather active and constantly forming and breaking bonds with its oxygens.

@@

To verify if the ``O'' coordination forms from, and breaks quickly to the unbound coordination as is suggested by the transition frequency plots in Figure \ref{fig:coordination-transitions}, we plot the lifespans of the various coordinations in Figure \ref{fig:coordination-lifespans}. Each point in the plot represents a time during the simulation in which the \suldiox~formed the respective coordination. The vertical ``lifespan'' position is calculated directly from the amount of time spent in the given coordination before changing to another. Both cold (blue) and hot (red) data are plotted. The data of Figure \ref{fig:coordination-lifespans} show that most coordination configurations last a very brief time, with the majority forming for under 0.5 ps. The three most populous coordinations, ``S'', ``SO'', ``SOO'' (as determined from Figure \ref{fig:bonding-coordinations} by percentage) in both temperatures have coordination lifetimes of up to 1 ps, in some instances lasting up to 1.5 ps. The brevity of lifespans overall speaks to the dynamic nature of the interface. The length of time in each coordination parallels the populations of the coordinations, and suggests an ordering of steady states among various bonding coordinations. The ``unbound'' configuration stands out as an anomaly amongst the lifespans of the other bonding coordinations. The few lifespans above 1.5 ps, up to 3.25 ps long, suggest a \suldiox~that not only unbinds from the water surface, but that it also recedes far enough to avoid a quick rebinding and coordination change to ``S'' or ``O''. Those few long lived unbound data points indicate times when the \suldiox~is far from the water, residing in the gas phase until the necessary water rearrangement occurs and it is drawn back to the surface to rebind.

@@

Returning to the transition plots of Figure \ref{fig:coordination-transitions}, the behavior of the unbound transition to both ``S'' and ``O'' coordination can now be better characterized. Figure \ref{fig:coordination-lifespans} shows that the ``O'' coordinated lifetimes are shorter than the ``S'' coordinated ones. Figure \ref{fig:coordination-transitions} shows that the unbound-``O'' transition occurs almost three times more than the transition to the ``S''. The unbound \suldiox~forms a bond to a neighboring water through its oxygen, but that bond is short-lived and either quickly breaks (resulting in unbound \suldiox), or it transitions to the ``SO'' coordination by forming another bond through the sulfur. The unbound-``S'' transition does not occur as often. This may be because the ``S'' coordination is more stable than the ``O''. Once in the ``S'' coordination the \suldiox~does not quickly break the interaction from its sulfur to water, but rather remains for up to 1 ps in the ``S'' coordination before (most likely) forming an oxygen bond to make the ``SO'' coordination. We have outlined the likely behavior of \suldiox~as it transitions from the gas phase in an unbound coordination to binding to an aqueous interface by forming bonds and interactions with surface waters.

Once the \suldiox~begins interacting with the water surface, the pathway leading back to the unbound coordination is not often traversed. As shown in Figure \ref{fig:coordination-transitions} the dominant coordination transitions occur between the ``S-SO-SOO'' group of coordinations. This suggests that the \suldiox-sulfur interaction to a water oxygen has a much longer lifespan than the oxygen bonding to water hydrogens. The difference between the ``S-SO-SOO'' coordinations is an addition or removal of oxygen bonds, and the frequent transitions between them show that the bonds to \suldiox-oxygens are quickly forming and breaking. For the \suldiox-sulfur interaction to break, the \suldiox~must enter a non-sulfur coordination (e.g. ``O'', ``OO'', unbound, etc.) or a coordination with more than a single sulfur interaction (e.g. ``SS'', ``SSO'', etc.). The transitions to coordinations that allow for breaking of the \suldiox-sulfur interactions, or switching the interaction to another water, are infrequent compared to those leading to an oxygen bond transition. Thus, the \suldiox~spends most of its time while bound to the surface waters breaking and forming hydrogen-bonds through its oxygens, and interacting with neighboring waters through a more persistent interaction via the \suldiox-sulfur atom.

>>>>

During the course of each simulation, the \suldiox~bonding coordination was determined and recorded for each timestep. From the coordination data we extract not only the populations of the various bonding coordinations, but also the frequencies of transitions between the different coordinations (i.e. the number of times each \suldiox~switched from one coordination type to another). With this data we have generated the directed graphs of Figure \ref{fig:coordination-transitions} depicting the cold and hot (Figure \ref{fig:coordination-transitions} A and B, respectively) bonding coordinations as circular colored nodes.\cite{Ellson2004,Gansner1999} The transitions between the coordinations are depicted as directed edges pointing in the direction of the transition from one bonding coordination to another. The populations of the coordinations are depicted by both the node size and coloration (larger and darker red coordinations occur more frequently). Populations of the transitions between coordinations are depicted by arrow thickness, with thicker lines corresponding to more frequent transitions. Additionally, the transition lines are numbered to the right of each line with the number of times each transition occurred.

@@

As expected for the more populated coordinations, there are more transitions between larger nodes in Figure \ref{fig:coordination-transitions} than transitions to less populated coordinations. Insights to the bonding process are made clearer from these graphs. In the cold system graph of Figure \ref{fig:coordination-transitions}A, we find that the majority of transitions are between the ``S-SO'' and ``SO-SOO'' nodes. The number of transitions within this ``S-SO-SOO'' group of bonding coordinations is an order of magnitude larger than any other transition. This indicates that while the \suldiox~is bound in any of the three most populated bonding coordinations, it is actively binding and unbinding the oxygens to form the other two coordinations in this group. Clearly, the \suldiox~is rather active and constantly forming and breaking bonds through its oxygens.

@@

To verify if the ``O'' coordination forms from, and breaks quickly to the unbound coordination as is suggested by the transition frequency plots in Figure \ref{fig:coordination-transitions}, we plot the lifespans of the various coordinations in Figure \ref{fig:coordination-lifespans}. Each point in the plot represents a time during the simulation in which the \suldiox~formed the respective coordination. The vertical ``lifespan'' position is calculated directly from the amount of time spent in the given coordination before changing to another. Both cold (blue) and hot (red) data are plotted. The data of Figure \ref{fig:coordination-lifespans} show that most coordination configurations last a very brief time, with the majority forming for under 0.5 ps. The three most populous coordinations, ``S'', ``SO'', ``SOO'' (as determined from Figure \ref{fig:bonding-coordinations} by percentage) in both temperatures have coordination lifetimes of up to 1 ps, in some instances lasting up to 1.5 ps. The brevity of lifespans overall speaks to the dynamic nature of the \suldiox~surface binding. The length of time in each coordination parallels the populations of the coordinations, and suggests an ordering of steady states among various bonding coordinations. The ``unbound'' configuration stands out as an anomaly amongst the lifespans of the other bonding coordinations. The few lifespans above 1.5 ps, up to 3.25 ps long, suggest a \suldiox~that not only unbinds from the water surface, but that it also recedes far enough to avoid a quick rebinding and coordination change to ``S'' or ``O''. Those few long lived unbound data points indicate times when the \suldiox~is far from the water, residing in the gas phase until the necessary water rearrangement occurs and it is drawn back to the surface to rebind.

@@

Returning to the transition plots of Figure \ref{fig:coordination-transitions}, the behavior of the unbound transition to both ``S'' and ``O'' coordination can now be better characterized. Figure \ref{fig:coordination-lifespans} shows that the ``O'' coordinated lifetimes are shorter than the ``S'' coordinated ones. Figure \ref{fig:coordination-transitions} shows that the unbound-``O'' transition occurs almost three times more than the transition to the ``S'' bonding coordination. The unbound \suldiox~forms a bond to a neighboring water through its oxygen, but that bond is short-lived and either quickly breaks (resulting in unbound \suldiox), or it transitions to the ``SO'' coordination by forming another bond through the sulfur. The unbound-``S'' transition does not occur as often. This may be because the ``S'' coordination is more stable than the ``O''. Once in the ``S'' coordination the \suldiox~does not quickly break the interaction from its sulfur to water, but rather remains for up to 1 ps in the ``S'' coordination before (most likely) forming an oxygen bond to make the ``SO'' coordination. We have outlined the likely behavior of \suldiox~as it transitions from the gas phase in an unbound coordination to binding to an aqueous interface by forming bonds and interactions with surface waters.

Once the \suldiox~begins interacting with the water surface, the pathway leading back to the unbound coordination is not often traversed. As shown in Figure \ref{fig:coordination-transitions} the dominant coordination transitions occur between the ``S-SO-SOO'' group of coordinations. This suggests that the \suldiox-sulfur interaction to a water oxygen has a much longer lifespan than the \suldiox-oxygen bonding to water hydrogens. The difference between the ``S-SO-SOO'' coordinations is an addition or removal of oxygen bonds, and the frequent transitions between them show that the bonds to \suldiox-oxygens are quickly forming and breaking. For the \suldiox-sulfur interaction to break, the \suldiox~must enter a non-sulfur coordination (e.g. ``O'', ``OO'', unbound, etc.) or a coordination with more than a single sulfur interaction (e.g. ``SS'', ``SSO'', etc.). The transitions to coordinations that allow for breaking of the \suldiox-sulfur interactions, or switching the interaction to another water, are infrequent compared to those leading to an oxygen bond transition. Thus, the \suldiox~spends most of its time while bound to the surface waters breaking and forming hydrogen-bonds through its oxygens, and interacting with neighboring waters through a more persistent interaction via the \suldiox-sulfur atom.

### 2011-11-30 Cycle-Results.tex
Conclusions! Finishing up the final edits before handing over to Geri.

\subsection{Cyclic \suldiox~Hydrate Structures}

Having examined the bonding coordinations and bonding behavior of \suldiox~with surface waters, we now turn to a secondary behavior of the hydrate structures that form around the surface-bound \suldiox~molecule. The simulation trajectory data was analyzed to determine the presence and characteristics of \suldiox~cyclic hydrate structures that form, as posited earlier in the text and depicted in Figure \ref{fig:cyclic-structures}. Only the most commonly occurring subset of the cyclic structures were analyzed based on two selection criteria: (1) The distances between atoms must match the same bonding/distance criteria as used for determining bonding coordinations. (2) The \suldiox~must be minimally in a bonding coordination of type ``SO'', meaning that the sulfur has at least one bonding interaction, and at least one hydrogen-bond must have formed with an oxygen to a neighboring water-hydrogen. As noted earlier in the discussion of the graph-finding routine and the BFS algorithm, the cyclic structures found represent the smallest cycles in which the \suldiox~is a member, based on the search's order of cycle discovery. The \suldiox~will be involved in other larger and more extended cyclic bonding structures beyond the first one discovered via the BFS. The larger and more extended cyclic structures involving more waters affect the behavior of the hydrogen-bonding network of the water surface. We focus here only on the smallest cycles involving the \suldiox~as they most affect the \suldiox~bonding and hydration.

@@

\subsection {Cyclic Structure Energy Calculations}

@@

We know that the \suldiox~bound to a water surface is most likely in the ``SO'' bonding coordination, and is also often taking part in some type of cyclic structure. With this in mind, it becomes interesting to ask: how long does a cyclic hydrate form before breaking to an acyclic hydrate structure? To answer the question of cyclic lifespan, a method was devised to define the lifetime of a cycle. For each MD trajectory, coordinate data was analyzed to determine if a cyclic hydrate structure was formed as described earlier in this manuscript. A timeline was then produced where each timestep was given a value of 1 or 0 depending on whether a particular \suldiox~hydrate bonding cycle was present or not, respectively. This resulted in a time-function, $C(t)$, similar in nature to a time-varying digital signal.

In an electro-mechanical system, a mechanical switch often outputs a noisy signal, full of transients or ``signal bounce'' before settling to a final value. This will appear as a rapid on-off cycling of the signal, and the problem is one of great concern in signal processing. Many mechanical, electrical, and software solutions have been devised to suppress the transients or ``debounce'' the signal. Analogously, the hydrate bonding cycles formed in the simulated system often undergo a period of time during formation, or before dissolution, where the $C(t)$ function bounces before settling into a final value. The bounce in the function, manifests itself in our statistics as a series of rapid switches between cycle presence and cycle absence. Physically, the bond lengths within the cycle (or the cycle-to-be) are fluctuating back and forth across our bond-length criteria. It is thus an artifact of our algorithmic determination of the presence or absence of a bond. Removing this artifact will allow us to examine the longer-time bonding behavior and this is accomplished as follows.

>>>>

\section {Cyclic \suldiox~Hydrate Structures}

Having examined the bonding coordinations and bonding behavior of \suldiox~with surface waters, we now turn to a secondary behavior of the hydrate structures that form around the surface-bound \suldiox~molecule. The simulation trajectory data was analyzed to determine the presence and characteristics of \suldiox~cyclic hydrate structures that form, as posited earlier in the text and depicted in Figure \ref{fig:cyclic-structures}. Only the most commonly occurring subset of the cyclic structures were analyzed based on two selection criteria: (1) The distances between atoms must match the same bonding/distance criteria as used for determining bonding coordinations. (2) The \suldiox~must be minimally in a bonding coordination of type ``SO'', meaning that the sulfur has at least one bonding interaction, and at least one hydrogen-bond must have formed with an oxygen to a neighboring water-hydrogen. As noted earlier in the discussion of the graph BFS algorithm, the cyclic structures found represent the smallest cycles in which the \suldiox~is a member, based on the search's order of cycle discovery. The \suldiox~will be involved in other larger and more extended cyclic bonding structures beyond the first one discovered via the BFS. The larger and more extended cyclic structures involving more waters affect the behavior of the hydrogen-bonding network of the water surface. We focus here only on the smallest cycles involving the \suldiox~as they most affect the \suldiox~bonding and hydration.

@@

@@

We know that the \suldiox~bound to a water surface is most likely in the ``SO'' bonding coordination, and is also often taking part in some type of cyclic structure. With this in mind, it becomes interesting to ask: how long does a cyclic hydrate form before breaking to an acyclic hydrate structure? To answer the question of cyclic lifespan, a method was devised to define the lifetime of a cycle. For each MD trajectory, coordinate data was analyzed to determine if a cyclic hydrate structure was formed as described earlier in this manuscript. A timeline was then produced where each timestep was given a value of 1 or 0 depending on whether a \suldiox~hydrate bonding cycle was present or not, respectively. This resulted in a time-function, $C(t)$, similar in nature to a time-varying digital signal.

In an electro-mechanical system, a mechanical switch often outputs a noisy signal, full of transients or ``signal bounce'' before settling to a final value. This will appear as a rapid on-off cycling of the signal, and the problem is one of great concern in signal processing. Many mechanical, electrical, and software solutions have been devised to suppress the transients, or ``debounce'' the signal. Analogously, the hydrate bonding cycles formed in the simulated system often undergo a period of time during formation, or before dissolution, where the $C(t)$ function bounces before settling into a final value. The bounce in the function manifests itself in our statistics as a series of rapid switches between cycle presence and cycle absence. Physically, the bond lengths within the cycle (or the cycle-to-be) are fluctuating back and forth across our bond-length criteria. It is thus an artifact of our algorithmic determination of the presence or absence of a bond. Removing this artifact will allow us to examine the longer-time bonding behavior and this is accomplished as follows.
